### 2014-08-12 Docs/flowchart/flowchart.tex
finish a pass through the flowchart chapter

Several authors \cite{KP:2012,VLBWZ:2013} explored the idea of energy
conservation in a low Mach number system and found that an additional
term (which can look like a buoyancy) is needed in the low Mach number
formulation, yielding:
\begin{equation}
\frac{\partial \Ub}{\partial t} + \Ub \cdot \nabla \Ub +
   \frac{\beta_0}{\rho} \nabla \left (\frac{p^\prime}{\beta_0} \right ) =
   -\frac{\rho^\prime}{\rho} |g| \er
\end{equation}
This is the form that we enforce in \maestro, and the choice is controlled
by \runparam{use\_alt\_energy\_fix}.

We decompose the full velocity field into a base state velocity,
$w_0$, that governs the base state dynamics, and a local velocity,
$\Ubt$, that governs the local dynamics, i.e., 
\begin{equation}
\Ub = w_0(r,t)\eb_r + \Ubt(\xb,t).
\end{equation}
with
$\overline{(\Ubt\cdot\eb_r)} = 0$ and
$w_0 = \overline{(\Ub\cdot\eb_r)}$---the motivation for this splitting was given in paper~II.
The velocity evolution equations are then 
\begin{eqnarray}
\frac{\partial w_0}{\partial t} &=& -w_0\frac{\partial w_0}{\partial
  r} - \frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r},\label{eq:w0
  evolution}\\ 
%
\frac{\partial\Ubt}{\partial t} &=& -(\Ubt + w_0\er)\cdot\nabla\Ubt
  - \left(\Ubt\cdot\eb_r\right)\frac{\partial w_0}{\partial r}\eb_r -
\frac{1}{\rho}\nabla\pi +
\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\eb_r -
\frac{\rho-\rho_0}{\rho}g\eb_r.\label{eq:flow:utildeupd}
\end{eqnarray}
where $\pi_0$ is the base state component of the perturbational pressure.
By laterally averaging to equation (\ref{eq:U divergence}),
we obtain a divergence constraint for $w_0$:
\begin{equation}
\nabla\cdot(\beta_0 w_0 \eb_r) = 
    \beta_0\left(\Sbar - \frac{1}{\gammabar p_0}
           \frac{\partial p_0}{\partial t}\right).\label{eq:w0 divergence}
\end{equation}
The divergence constraint for $\Ubt$ can be found by subtracting
(\ref{eq:w0 divergence}) into (\ref{eq:U divergence}), resulting in
\begin{equation}
\nabla\cdot\left(\beta_0\Ubt\right) = \beta_0\left(S-\Sbar\right).\label{eq:utilde divergence}
\end{equation}

@@

@@

\item Compute the base state velocity forcing.  Rearrange equation (\ref{eq:pizero}),
\begin{equation}
\left ( \frac{1}{\rho_0} \frac{\partial \pi_0}{\partial r} \right )^n = 
-\frac{w_0^{\nph} - w_0^\nmh}{\myhalf(\dt^n+\dt^{n-1})} 
- w_0^n \left(\frac{\partial w_0}{\partial r}\right)^n,
\end{equation}
  where $w_0^{n}$ and $(\partial w_0 / \partial r)^{n}$ are defined as
\begin{eqnarray}
w_0^n &=& \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph}}{\dt^n+\dt^{n-1}}, \\
\left(\frac{\partial w_0}{\partial r}\right)^{n} &=& \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh} + \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph} \right ].\nonumber \\
\end{eqnarray}
  If $n=0$, we use $\dt^{-1} = \dt^0$.

@@

\item Update the temperature using the equation of state:
$T^{(2)} = 
   T(\rho^{(2)}, h^{(2)}, X_k^{(2)})$ (planar geometry) or
$T^{(2)} = 
   T(\rho^{(2)}, p_0^{n+1}, X_k^{(2)})$ (spherical geometry).
\end{enumerate}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \Alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho^{n+1} p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)}  
   + \sigma \Hext^{(2)},
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the thermodynamic quantities are defined using $\rho^{n+1}$,
$X_k^{n+1}$, and $T^{n+1}$ as inputs to the equation of state.
Then, compute
\begin{equation}
\overline{S^{n+1}} = {\mathrm{\bf Avg}} (S^{n+1}).
\end{equation}

@@

First, we compute the time-centered edge velocities, $\Ubt^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ubt^n$ to $\Ubt^{n+1,\dagger}$ by discretizing 
equation (\ref{eq:flow:utildeupd}) as
\begin{eqnarray}
\Ubt^{n+1,\dagger} 
&=& \Ubt^n - \dt \left[\left(\uadvtwo+ w_0^{\nph} \eb_r\right) \cdot \nabla \Ubt^{\nph,\pred} \right] \nonumber \\
&&- \dt \left(\uadvtwo \cdot \eb_r\right)  \left(\frac{\partial w_0}{\partial r} \right)^\nph \eb_r \nonumber \\
&& + \dt \left[ - \frac{1}{\rho^\nph} \mathbf{G} \pi^\nmh + \left(\frac{1}{\rho_0}\frac{\partial\pi_0}{\partial r}\right)^n \eb_r - \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],\nonumber \\
\end{eqnarray}
where $\mathbf{G}$ approximates a cell-centered gradient from nodal
data.  Again, the $\dagger$ superscript refers 
to the fact that the updated velocity does not satisfy the divergence 
constraint.

@@

\subsection{Volume Discrepancy Changes}
\begin{itemize}
\item In {\bf Step 2B}, to compute $w_0$, we need to account for the volume discrepancy
term by first defining $p_{\rm EOS}^n = \overline{p(\rho,h,X_k)^n}$, and then using:
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} = \overline{S^{\nph,\star\star}} - \frac{1}{\overline{\Gamma_1^n}p_0^n}\psi^{\nmh} - \underbrace{\frac{f}{\overline{\Gamma_1^n}p_0^n}\left(\frac{p_0^n-\overline{p_{\rm EOS}^n}}{\Delta t}\right)}_{\delta\chi_{w_0}}.
\end{equation}
\item In {\bf Step 3}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left[ \left(S^{\nph,\star\star} - \overline{S^{\nph,\star\star}}\right)
+ \underbrace{\frac{f}{\gammabar^n p_0^n}
\left(\frac{p_{\rm EOS}^n - \overline{p_{\rm EOS}^n}}{\Delta t^n}\right)}_{\delta\chi}\right].
\end{equation}
\item In {\bf Step 6B}, to compute $w_0$, we need to account for the volume discrepancy
term by first defining $p_{\rm EOS}^{n+1,\star} = p(\rho,h,X_k)^{n+1,\star}$,
$\overline{\Gamma_1^{\nph,\star}} = (\overline{\Gamma_1^{n}}+\overline{\Gamma_1^{n+1,\star}})/2$,
and $p^{\nph,\star} = (p^{n}+p^{n+1,\star})/2$, and then using:
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = \overline{S^{\nph,\star}} - \frac{1}{\overline{\Gamma_1^{\nph,\star}}p_0^{\nph,\star}}\psi^{\nph,\star} - \frac{f}{\overline{\Gamma_1^{n+1,\star}}p_0^{n+1,\star}}\left(\frac{p_0^{n+1,\star}-\overline{p_{\rm EOS}^{n+1,\star}}}{\Delta t}\right) - \delta\chi_{w_0}
\end{equation}
\item In {\bf Step 7}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) = \beta_0^{\nph,\star}\left[\left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) + \frac{f}{\overline{\Gamma_1^{n+1,\star}} p_0^{n+1,\star}} \left(\frac{p_{\rm EOS}^{n+1,\star} - \overline{p_{\rm EOS}^{n+1,\star}}}{\Delta t^n}\right) + \delta\chi\right],
\end{equation}
where $p(\rho,h,X_k)^{\nph,\star} = \left[p(\rho,h,X_k)^n +p(\rho,h,X_k)^{n+1,\star}\right]/2$.
\item In {\bf Step 11}, the approximate projection should account for the volume
discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\overline{\Gamma_1^{n+1}} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}.
\end{equation}
\end{itemize}

@@

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then have
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 = S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ub \cdotb \nablab p_0 \enskip , \label{eq:gammafull}
\end{equation}
The base state evolution equation is the average of this over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \ut \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}

These can be written more compactly as:
\begin{equation}
\frac{\partial w_0}{\partial r} = \Sbar -\frac{1}{\gammabar p_0}\psi +
\overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab
  p_0 \right ) } \enskip , \label{eq:base_w0_with_dgamma1}
\end{equation}
for plane-parallel geometries (analogous to eq. [\ref{eq:divw0}]), and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt) = \beta_0 \left [ S - \Sbar + \frac{\delta
    \Gamma_1}{\gammabar^2 p_0} \psi + \frac{\delta \Gamma_1}{\gammabar^2 p_0}
  \Ubt \cdotb \nablab p_0 - \overline{ \left ( \frac{\delta
      \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0 \right ) } ~ \right ]
 \enskip ,  \label{eq:constraint_with_delta_gamma}
\end{equation}

@@

%-----------------------------------------------------------------------------
\subsection{Thermal Diffusion Changes}
Immediately after {\bf Step 4H}, diffuse the enthalpy through 
a time interval of $\dt$.  First, define $(\rho h)^{(1a),\star} = (\rho h)^{(2),\star}$.  
We recompute $(\rho h)^{(2),\star}$ to account for thermal diffusion.  Here we begin
with the enthalpy equation, but consider only the 
diffusion terms,
\begin{equation}
\frac{\partial (\rho h)}{\partial t} = \nabla\cdot\kth\nabla T.
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0.
  \end{equation}
Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}

@@

\subsection{Changes Between the Multilevel Paper and Paper 5}
\begin{enumerate}
\item Added rotation.
\end{enumerate}

@@

>>>>

Several authors \cite{KP:2012,VLBWZ:2013} explored the idea of energy
conservation in a low Mach number system and found that an additional
term (which can look like a buoyancy) is needed in the low Mach number
formulation, yielding:
\begin{equation}
\frac{\partial \Ub}{\partial t} + \Ub \cdot \nabla \Ub +
   \frac{\beta_0}{\rho} \nabla \left (\frac{p^\prime}{\beta_0} \right ) =
   -\frac{\rho^\prime}{\rho} |g| \er
\label{eq:flow:newmomentum}
\end{equation}
This is the form that we enforce in \maestro, and the choice is controlled
by \runparam{use\_alt\_energy\_fix}.

We decompose the full velocity field into a base state velocity,
$w_0$, that governs the base state dynamics, and a local velocity,
$\Ubt$, that governs the local dynamics, i.e., 
\begin{equation}
\Ub = w_0(r,t)\eb_r + \Ubt(\xb,t).
\end{equation}
with
$\overline{(\Ubt\cdot\eb_r)} = 0$ and
$w_0 = \overline{(\Ub\cdot\eb_r)}$---the motivation for this splitting was given in paper~II.
The velocity evolution equations are then 
\begin{eqnarray}
\frac{\partial w_0}{\partial t} &=& -w_0\frac{\partial w_0}{\partial
  r} - \frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r},\label{eq:w0
  evolution}\\ 
%
\frac{\partial\Ubt}{\partial t} &=& -(\Ubt + w_0\er)\cdot\nabla\Ubt
  - \left(\Ubt\cdot\eb_r\right)\frac{\partial w_0}{\partial r}\eb_r -
\frac{\beta_0}{\rho}\nabla\left(\frac{\pi}{\beta_0} \right) +
\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\eb_r -
\frac{\rho-\rho_0}{\rho}g\eb_r.\label{eq:flow:utildeupd}
\end{eqnarray}
where $\pi_0$ is the base state component of the perturbational pressure.
By laterally averaging to equation (\ref{eq:U divergence}),
we obtain a divergence constraint for $w_0$:
\begin{equation}
\nabla\cdot(\beta_0 w_0 \eb_r) = 
    \beta_0\left(\Sbar - \frac{1}{\gammabar p_0}
           \frac{\partial p_0}{\partial t}\right).\label{eq:w0 divergence}
\end{equation}
The divergence constraint for $\Ubt$ can be found by subtracting
(\ref{eq:w0 divergence}) into (\ref{eq:U divergence}), resulting in
\begin{equation}
\nabla\cdot\left(\beta_0\Ubt\right) = \beta_0\left(S-\Sbar\right).\label{eq:utilde divergence}
\end{equation}

@@

When we are using thermal diffusion, there will be an additional term in
the enthalpy equation (see \S~\ref{sec:flow:diffusion}).

@@

\item Compute the base state velocity forcing.  Rearrange equation (\ref{eq:pizero}),
\begin{equation}
\left ( \frac{\beta_0}{\rho_0} \frac{\partial (\pi_0/\beta_0)}{\partial r} \right )^n = 
-\frac{w_0^{\nph} - w_0^\nmh}{\myhalf(\dt^n+\dt^{n-1})} 
- w_0^n \left(\frac{\partial w_0}{\partial r}\right)^n,
\end{equation}
  where $w_0^{n}$ and $(\partial w_0 / \partial r)^{n}$ are defined as
\begin{eqnarray}
w_0^n &=& \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph}}{\dt^n+\dt^{n-1}}, \\
\left(\frac{\partial w_0}{\partial r}\right)^{n} &=& \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh} + \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph} \right ].\nonumber \\
\end{eqnarray}
  If $n=0$, we use $\dt^{-1} = \dt^0$.

@@

\item Update the temperature using the equation of state:
$T^{(2)} = 
   T(\rho^{(2)}, h^{(2)}, X_k^{(2)})$ (planar geometry) or
$T^{(2)} = 
   T(\rho^{(2)}, p_0^{n+1}, X_k^{(2)})$ (spherical geometry).
\end{enumerate}
Again, the actual inputs depend of \runparam{use\_tfromp}.

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \Alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho^{n+1} p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)}  
   + \sigma \Hext^{(2)},
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the thermodynamic quantities are defined using $\rho^{n+1}$,
$X_k^{n+1}$, and $T^{n+1}$ as inputs to the equation of state.
If we are doing thermal diffusion (\runparam{use\_thermal\_diffusion}{\tt = T})
then we also include the diffusive term in $S$.
Then, compute
\begin{equation}
\overline{S^{n+1}} = {\mathrm{\bf Avg}} (S^{n+1}).
\end{equation}

@@

First, we compute the time-centered edge velocities, $\Ubt^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ubt^n$ to $\Ubt^{n+1,\dagger}$ by discretizing 
equation (\ref{eq:flow:utildeupd}) as
\begin{eqnarray}
\Ubt^{n+1,\dagger} 
&=& \Ubt^n - \dt \left[\left(\uadvtwo+ w_0^{\nph} \eb_r\right) \cdot \nabla \Ubt^{\nph,\pred} \right] \nonumber \\
&&- \dt \left(\uadvtwo \cdot \eb_r\right)  \left(\frac{\partial w_0}{\partial r} \right)^\nph \eb_r \nonumber \\
&& + \dt \left[ - \frac{\beta_0^\nph}{\rho^\nph} \mathbf{G} \left ( \frac{\pi}{\beta_0}\right)^\nmh + \left(\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\right)^n \eb_r - \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],\nonumber \\
\end{eqnarray}
where $\mathbf{G}$ approximates a cell-centered gradient from nodal
data.  Again, the $\dagger$ superscript refers 
to the fact that the updated velocity does not satisfy the divergence 
constraint.

@@

\subsection{Volume Discrepancy Changes}

Chapter~\ref{ch:volume} describes the reasoning behind the volume discrepancy
term---a forcing term added to the constraint equation to bring us back to
the equation of state.  This addition of this term (enabled with \runparam{dpdt\_factor}{\tt = T}) modifies our
equation set in the following way:

\begin{itemize}
\item In {\bf Step 2B}, to compute $w_0$, we need to account for the volume discrepancy
term by first defining $p_{\rm EOS}^n = \overline{p(\rho,h,X_k)^n}$, and then using:
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} = \overline{S^{\nph,\star\star}} - \frac{1}{\overline{\Gamma_1^n}p_0^n}\psi^{\nmh} - \underbrace{\frac{f}{\overline{\Gamma_1^n}p_0^n}\left(\frac{p_0^n-\overline{p_{\rm EOS}^n}}{\Delta t}\right)}_{\delta\chi_{w_0}}.
\end{equation}
\item In {\bf Step 3}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left[ \left(S^{\nph,\star\star} - \overline{S^{\nph,\star\star}}\right)
+ \underbrace{\frac{f}{\gammabar^n p_0^n}
\left(\frac{p_{\rm EOS}^n - \overline{p_{\rm EOS}^n}}{\Delta t^n}\right)}_{\delta\chi}\right].
\end{equation}
\item In {\bf Step 6B}, to compute $w_0$, we need to account for the volume discrepancy
term by first defining $p_{\rm EOS}^{n+1,\star} = p(\rho,h,X_k)^{n+1,\star}$,
$\overline{\Gamma_1^{\nph,\star}} = (\overline{\Gamma_1^{n}}+\overline{\Gamma_1^{n+1,\star}})/2$,
and $p^{\nph,\star} = (p^{n}+p^{n+1,\star})/2$, and then using:
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = \overline{S^{\nph,\star}} - \frac{1}{\overline{\Gamma_1^{\nph,\star}}p_0^{\nph,\star}}\psi^{\nph,\star} - \frac{f}{\overline{\Gamma_1^{n+1,\star}}p_0^{n+1,\star}}\left(\frac{p_0^{n+1,\star}-\overline{p_{\rm EOS}^{n+1,\star}}}{\Delta t}\right) - \delta\chi_{w_0}
\end{equation}
\item In {\bf Step 7}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) = \beta_0^{\nph,\star}\left[\left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) + \frac{f}{\overline{\Gamma_1^{n+1,\star}} p_0^{n+1,\star}} \left(\frac{p_{\rm EOS}^{n+1,\star} - \overline{p_{\rm EOS}^{n+1,\star}}}{\Delta t^n}\right) + \delta\chi\right],
\end{equation}
where $p(\rho,h,X_k)^{\nph,\star} = \left[p(\rho,h,X_k)^n +p(\rho,h,X_k)^{n+1,\star}\right]/2$.
\item In {\bf Step 11}, the approximate projection should account for the volume
discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\overline{\Gamma_1^{n+1}} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}.
\end{equation}
\end{itemize}

@@

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then have \MarginPar{I think that we include to $\delta \Gamma_1^2$ now}
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 = S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ub \cdotb \nablab p_0 \enskip , \label{eq:gammafull}
\end{equation}
The base state evolution equation is the average of this over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \ut \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}

These can be written more compactly as:
\begin{equation}
\frac{\partial w_0}{\partial r} = \Sbar -\frac{1}{\gammabar p_0}\psi +
\overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab
  p_0 \right ) } \enskip , \label{eq:base_w0_with_dgamma1}
\end{equation}
for plane-parallel geometries (analogous to
Eq.~\ref{eq:flow:dw0dr_planar}), and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt) = \beta_0 \left [ S - \Sbar + \frac{\delta
    \Gamma_1}{\gammabar^2 p_0} \psi + \frac{\delta \Gamma_1}{\gammabar^2 p_0}
  \Ubt \cdotb \nablab p_0 - \overline{ \left ( \frac{\delta
      \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0 \right ) } ~ \right ]
 \enskip ,  \label{eq:constraint_with_delta_gamma}
\end{equation}

@@

%-----------------------------------------------------------------------------
\subsection{Thermal Diffusion Changes}

\label{sec:flow:diffusion}

Thermal diffusion was introduced in the XRB paper~\cite{xrb}.  This
introduces a new term to $S$ as well as the enthalpy equation.
Treating the enthalpy equation now requires a parabolic solve.  We describe
that process here.

Immediately after {\bf Step 4H}, diffuse the enthalpy through 
a time interval of $\dt$.  First, define $(\rho h)^{(1a),\star} = (\rho h)^{(2),\star}$.  
We recompute $(\rho h)^{(2),\star}$ to account for thermal diffusion.  Here we begin
with the enthalpy equation, but consider only the 
diffusion terms,
\begin{equation}
\frac{\partial (\rho h)}{\partial t} = \nabla\cdot\kth\nabla T.
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0.
  \end{equation}
Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}

@@

\subsection{Changes Between the Multilevel Paper and Paper 5~\cite{wdconvect}}
\begin{enumerate}
\item Added rotation.
\end{enumerate}

@@

\subsection{Changes Since the XRB Paper}

\begin{enumerate}

\item We switched to the new form of the momentum equation to
Eq.~\ref{eq:flow:newmomentum} to conserve the low-Mach number form of
energy.

\item We changed the form of the volume discrepancy term to get better
agreement between the two temperatures.
